Lifauo Amicus Brief Models

### 2022-04-27 modeling/amicus_type/lifauo.Rmd
close #30

```{r}
data <- box_read(full_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(lifauo_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
```

@@

```{r}
data_scale <- data %>%
  mutate(across(c(where(is.numeric), -justicevot, -id),
                ~(scale(., center=T, scale=T) %>% as.vector)))

data_scale <- janitor::remove_empty(data_scale, which = "cols")
```

@@

* 0:
* 0.01:
* 0.05: physician negative, privacy
* 0.10: fetus, final authority,

@@

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_abortion_different,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

# Abortion Immoral

```{r}
mod2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_abortion_immoral,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod2)
```

# Anti-Women

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_anti_women,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

# Bodily Integrity

```{r}
mod5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_bodily_integrity,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod5)
```

@@

```{r}
mod6a <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_compulsory_motherhood,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod6b <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_compulsory_motherhood_ii,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

# Couple

```{r}
mod7 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_couple,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod7)
```

# Eql Protection

```{r}
mod8 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_equal_protection,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod8)
```

@@

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

# Favor Childbirth

```{r}
mod10 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_favor_childbirth,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod10)
```

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod11)
```

@@

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

# Informed Consent

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_informed_consent,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

# Intersectionality

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_intersectionality,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod13)
```

@@

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

# Physician

```{r}
mod16 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_physician,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod16)
```

# Physician Negative

```{r}
mod17 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_physician_negative,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod17)
```

@@

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

# Protesters

```{r}
mod19 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_protesters,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod19)
```

@@

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

# State Interest

```{r}
mod21 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_state_interest,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

summary(mod21)
```

@@

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

>>>>

```{r}
data <- box_read(final_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2),
         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
         lcdisdirfem = as.factor(lcdisdirfem),
         cirsplit = as.factor(cirsplit)) %>% 
  mutate(across(c(lifauo_abortion_different:lifauo_womens_rights), ~replace_na(.x, 0)))
```

@@

```{r}
data <- data %>%
  select(case:cirsplit, poppam, lifauo_abortion_different:lifauo_womens_rights) %>% 
  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
                ~(scale(., center=T, scale=T))))
                #~(scale(., center=T, scale=T) %>% as.vector)))

total_cols <- data %>% select(contains('lifauo')) %>% colnames()
data <- janitor::remove_empty(data, which = "cols")
remaining_cols <- data %>% select(contains('lifauo')) %>% colnames()
setdiff(total_cols, remaining_cols)
```

@@

* 0:
* 0.01:
* 0.05: 
* 0.10: final authority, privacy

@@

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_abortion_different + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod1,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

@@

# Abortion Regret

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_abortion_regret + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod3,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

@@

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_bad_law + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod4,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

@@

@@

```{r}
mod6a <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_compulsory_motherhood + poppam,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod6a,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

@@

```{r}
mod6b <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_compulsory_motherhood_ii + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod6b,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

@@

@@

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_evidence + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod9,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

@@

@@

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_final_authority + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod12,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

@@

@@

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_morality_religion + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod14,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

@@

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_overturn_roe + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod15,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

@@

@@

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_privacy + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod18,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

@@

@@

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_standing + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod20,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

@@

@@

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_uncertainty + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod22,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

@@

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_undue_burden + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod23,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

@@

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_untruthful + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod24,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

@@

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_womens_future_life + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod25,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

@@

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_womens_health + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod26,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

@@

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                lifauo_womens_rights + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod27,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()
